Wikipedia Text Mining and Entropy Analysis

### 2019-01-09 wiki_entropy/wiki_clustering.Rmd
initial clusteval code
initial clusteval code - with edits

```{r clustering}
##read in googlesheet
wiki_gs <- gs_title("Wikipedia_absolute")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

@@

##do clustering
wk_clust <- wkpd %>% 
              dist() %>%
              hclust("ward.D2")

wk_clust %>% plot(hang = -1)
```

@@

imputed_wf <- as.data.frame(rv[[1]][[99]])
```

>>>>

```{r clustering}
NUM_CLUSTERS <- 10

##read in googlesheet
wiki_gs <- gs_title("Wikipedia_absolute")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

@@

##do clustering
wk_clust_tree <- wkpd %>% 
              dist() %>%
              hclust("ward.D2")

wk_clust_tree %>% plot(hang = -1)
wk_clusters <- wk_clust_tree %>%
              cutree(k = NUM_CLUSTERS)
```

@@

imputed_wf <- as.data.frame(rv[[1]][[99]])

wals_clust_full <- kmodes(imputed_wf, NUM_CLUSTERS, iter.max=10, weighted = FALSE)
```

```{r evaluate_clusters}
wals_clusters <- wals_clust["cluster"] %>% unlist(use.names= FALSE)
```
